M-M paper, morphological bias

### 2015-03-25 papers/MbhMsph/mm.tex
wed

\section{Data}
\label{sec:data}
Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Our state-of-the-art galaxy decompositions take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
We have additionally used kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
Details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
together with the individual 66 galaxy decompositions, will be presented in \emph{Paper I}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}

>>>>

\section{Data}
\label{sec:data}
Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge luminosities were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
and illustrate the individual 66 galaxy decompositions.

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
%\caption{}
%\label{fig:}
%\end{center}
%\end{figure}

\section{Analysis}
\label{sec:anal}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}
